Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-06 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

Although there is no quantum cryptodeterministic measure defined on
$\mathcal{T}_{24}$, it is easy to construct a real-valued probability
measure by the Born rule, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}|_{\events_{24}}$.

>>>>

On one hand, the Kochen-Specker theorem is equivalent to non-existence
of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
where $\events$ is the set of all projections on a Hilbert space.
On the other hand, if the range is the interval~$\left[0,1\right]$,
Gleason's theorem asserts that every quantum real-valued probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
by a density matrix according to the Born rule. These two extreme
cases can be understood in a broader framework of quantum interval-valued
probability~$\bar{\mu}:\events\rightarrow\mathscr{I}$, where $\mathscr{I}$
is a collection of intervals containing in $\left[0,1\right]$. When
we pick $\mathscr{I}$ as $\left\{ \imposs,\necess\right\} $, where
$\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$, there
is no quantum interval-valued probability~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem.

Although there is no quantum cryptodeterministic measure defined on
$\mathcal{T}_{24}$, it is easy to construct a real-valued probability
measure by the Born rule, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}|_{\events_{24}}$.\footnote{\yutsung{{Find all orthogonal basis of }$\mathcal{T}_{24}$ and solve
the linear equations for Gleason's...}}
